---
title: "Viz and EDA"
subtitle 
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
library(hexbin)
data("weather_df")
```


##scatterplots

First scatterplot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

New approach same plot
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit a plot object
```{r}
weather_plot = 
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_plot + geom_point()
```

##advanced scatterplot

Start w the same one and mae it fancy
this makes 3 different geom smooth lines 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

```

AES placement?
color here only applies to teh scatterplot 
this makes 1 line

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) + 
  geom_smooth()

```

Facet  now separates out by name 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)

```

switch up rows and columns
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  facet_grid(name ~.)
```

adjust alpha level 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.2, size = 2) + 
  geom_smooth(se = FALSE) + 
  facet_grid(name ~.)
```

New plot
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name )) + 
  geom_point(alpha = 0.2) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~name)
```


## small notes

how many geoms have to exist? 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)

```


neat geom
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_hex()
```


neat geom
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_density2d() +
  geom_point(alpha = 0.3)
```


## Univariate plots

Histogram
```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) + 
  geom_histogram()
```

add color
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, color = name)) + 
  geom_histogram()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, color = name)) + 
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge")
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge") +
  facet_grid(. ~name)
```

New geom!
w
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.3, adjust = 0.5)

```

Boxplots

```{r}
weather_df %>% 
  ggplot(aes(x= name, y = tmin)) +
  geom_boxplot()
```

trendy plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = 0.5) +
  stat_summary()
```


Ridge plots the most popular
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y=name)) +
  geom_density_ridges()
```

